\documentclass[
      a4paper,
        12pt,
          oneside,
      ]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsmath,textcomp,tikz,float,pgf,hyperref,setspace,xcolor}

  \usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}


\setcounter{secnumdepth}{4}
\setlength{\headheight}{25pt}

  \usepackage{scrlayer-scrpage}
  \ihead{Session May 2021}
  \chead{IBDP Extended Essay}
  \ohead{Economics}
  \ifoot{}
  \cfoot{\thepage}
  \ofoot{}

  \doublespacing

\providecommand{\tightlist}{
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
}

  \usepackage{lmodern}



  \usepackage{euler}

  \title{
    \textbf{Road Pricing for Luxembourg}\\
    \emph{Should Luxembourg introduce road user charges?}
      }
  \author{
          Nico Bachner\\
          Candidate Number: 123456 123
        }
  \date{\today}

%  ____
% |     \
% |  |\  \
% |  | \  \
% |  |\ \  \  
% |  |_\_\  \
% |   ____   \
% |  |___| \  \
% |  |    \ \  \  
% |__|     \ \__\
% |__|      \|__|

\begin{document}

\maketitle
\thispagestyle{empty}

  \begin{abstract}
    \ldots{}
  \end{abstract}

      \newpage
        \setcounter{tocdepth}{4}
    \tableofcontents
      \newpage
  


\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{reasons-for-choice}{%
\subsection{Reasons for choice}\label{reasons-for-choice}}

Road pricing is a personal interest of mine. Since I am an avid cyclist,
I dislike overly congested streets. They pollute the air and waste many
people's time.

\hypertarget{outline}{%
\subsection{Outline}\label{outline}}

\begin{itemize}
\tightlist
\item
  Reasons for road pricing

  \begin{itemize}
  \tightlist
  \item
    Traffic jams
  \item
    Accidents
  \item
    Pollution
  \item
    Government income
  \end{itemize}
\item
  Probe elasticity of automobile usage in Luxembourg
\item
  Explore changes in behaviour as a result of road pricing

  \begin{itemize}
  \tightlist
  \item
    Impact on traffic jams
  \item
    Impact on accidents
  \item
    Impact on pollution
  \end{itemize}
\item
  Explore impact on individual social classes
\item
  Will a congestion charge increase social inequality?
\item
  Complications and issues to be resolved

  \begin{itemize}
  \tightlist
  \item
    Will delivery services be exempt from the tax?
  \item
    Compare to other cities
  \item
    Costs vs benefits
  \item
    What methods to use to enable and enforce charges?
  \item
    Political viability and public opinion
  \item
    Impact of the ``frontaliers''
  \end{itemize}
\end{itemize}

\hypertarget{road-pricing}{%
\section{Road Pricing}\label{road-pricing}}

\hypertarget{a-brief-history-of-road-pricing}{%
\subsection{A brief History of Road
Pricing}\label{a-brief-history-of-road-pricing}}

\ldots{}

\hypertarget{the-current-state-of-road-pricing}{%
\subsection{The Current State of Road
Pricing}\label{the-current-state-of-road-pricing}}

\hypertarget{globally}{%
\subsubsection{Globally}\label{globally}}

\begin{itemize}
\tightlist
\item
  Cities that have implemented road pricing:

  \begin{itemize}
  \tightlist
  \item
    London
  \item
    Stockholm
  \item
    Singapore
  \item
    Milan
  \end{itemize}
\end{itemize}

\hypertarget{in-luxembourg}{%
\subsubsection{In Luxembourg}\label{in-luxembourg}}

\begin{itemize}
\tightlist
\item
  Traffic jams
\item
  Accidents
\item
  Pollution
\end{itemize}

\hypertarget{hypothesis}{%
\section{Hypothesis}\label{hypothesis}}

\begin{itemize}
\tightlist
\item
  Introducing a road user charge will have an overall positive outcome
  due to it decreasing automobile use, thus decreasing negative factors
  such as pollution and time waste through traffic jams
\end{itemize}

\hypertarget{results}{%
\section{Results}\label{results}}

\ldots{}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\ldots{}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\ldots{}

\hypertarget{references}{%
\section{References}\label{references}}

Khan Academy, (2019). \emph{Macroeconomics}. {[}online{]} Available at:
\url{https://www.khanacademy.org/economics-finance-domain/macroeconomics}
{[}Accessed 2 June 2019{]}\\
Smeed, R.J., 1968. Traffic studies and urban congestion. Journal of
Transport Economics and Policy, pp.33-70.\\
Sharp, C., 1966. Congestion and Welfare-an Examination of the Case for a
Congestion Tax.\,The Economic Journal,\,76(304), pp.806-817.\\
Beesley, M.E., 1965. The value of time spent in travelling: some new
evidence.\,Economica,\,32(126), pp.174-185.\\
Richardson, H.W., 1974. A note on the distributional effects of road
pricing.\,Journal of Transport Economics and Policy, pp.82-85.\\
Derbel, A. and Boujelbene, Y., 2019, October. A Systematic Literature
Review of Studies on Road Congestion Modelling. In\,International
Workshop on Distributed Computing for Emerging Smart
Networks\,(pp.~23-36). Springer, Cham. Fridstrøm, L., The Case for
Marginal Cost Road Pricing in Norway.\\
Meloche, J.P., 2019.\,Towards a New Era in Road Pricing? Lessons from
the Experience of First Movers\,(No.~2019s-35). CIRANO.

\hypertarget{rppf}{%
\section{RPPF}\label{rppf}}

\end{document}