\documentclass[
      a4paper,
        12pt,
          oneside,
      ]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsmath,scrlayer-scrpage,textcomp,tikz,float,pgf,hyperref,setspace,xcolor}

\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}

\setcounter{secnumdepth}{4}
\setlength{\headheight}{25pt}

  \doublespacing

\providecommand{\tightlist}{
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
}

\usepackage{lmodern}



  \usepackage{scrlayer-scrpage}
  \ihead{Session May 2021} 
  \chead{IBDP Extended Essay} 
  \ohead{Economics}
  \cfoot{\thepage}

  \title{
    Luxembourg Congestion Charge
      }
  \author{
          Nico Bachner \textbar{} Candidate Number: 123456 123
        }
  \date{\today}




\begin{document}

\maketitle

  \begin{abstract}
    yefhwd df dfs
  \end{abstract}




\maketitle
\thispagestyle{empty}
\newpage
\tableofcontents
\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\begin{itemize}
\tightlist
\item
  Reasons for choice
\item
  Introduction to topic

  \begin{itemize}
  \tightlist
  \item
    Generic facts about Luxembourg's road usage

    \begin{itemize}
    \tightlist
    \item
      Traffic jams
    \item
      Accidents
    \item
      Pollution
    \end{itemize}
  \item
    What is a congestion tax?

    \begin{itemize}
    \tightlist
    \item
      Introduce the concept of road pricing
    \end{itemize}
  \item
    Generic facts about Luxembourg's road usage
  \end{itemize}
\item
  Hypothesis:

  \begin{itemize}
  \tightlist
  \item
    Introducing a congestion charge will have an overall positive
    outcome due to it decreasing automobile use and thus decreasing
    negative factors such as pollution and time waste through traffic
    jams
  \end{itemize}
\item
  Plan:

  \begin{itemize}
  \tightlist
  \item
    Traffic jams
  \item
    Accidents
  \item
    Pollution
  \end{itemize}
\end{itemize}

\hypertarget{main-body}{%
\section{Main Body}\label{main-body}}

\begin{itemize}
\tightlist
\item
  Probe elasticity of automobile usage in Luxembourg
\item
  Explore changes in behaviour as a result of road pricing

  \begin{itemize}
  \tightlist
  \item
    Impact on traffic jams
  \item
    Impact on accidents
  \item
    Impact on pollution
  \end{itemize}
\item
  Explore impact on individual social classes
\item
  Will a congestion charge increase social inequality?
\item
  Complications and issues to be resolved

  \begin{itemize}
  \tightlist
  \item
    Will delivery services be exempt from the tax?
  \item
    Compare to other cities
  \item
    Costs vs benefits
  \item
    What methods to use to enable and enforce charges?
  \item
    Political viability and public opinion
  \item
    Impact of the ``frontaliers''
  \end{itemize}
\end{itemize}

\hypertarget{the-transportation-sector-in-luxembourg-as-of-2020}{%
\subsection{The transportation sector in Luxembourg as of
2020}\label{the-transportation-sector-in-luxembourg-as-of-2020}}

In order to determine how introducing a congestion charge will impact
the Luxembourg economy, we first need to understand how the
transportation sector currently functions.

\hypertarget{impact-of-a-congestion-charge}{%
\subsection{Impact of a congestion
charge}\label{impact-of-a-congestion-charge}}

m

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

test

\hypertarget{references}{%
\section{References}\label{references}}

Khan Academy, (2019). \emph{Macroeconomics}. {[}online{]} Available at:
\url{https://www.khanacademy.org/economics-finance-domain/macroeconomics}
{[}Accessed 2 June 2019{]}

Smeed, R.J., 1968. Traffic studies and urban congestion. Journal of
Transport Economics and Policy, pp.33-70.

Sharp, C., 1966. Congestion and Welfare-an Examination of the Case for a
Congestion Tax.\,The Economic Journal,\,76(304), pp.806-817.

Beesley, M.E., 1965. The value of time spent in travelling: some new
evidence.\,Economica,\,32(126), pp.174-185.

Richardson, H.W., 1974. A note on the distributional effects of road
pricing.\,Journal of Transport Economics and Policy, pp.82-85.

Derbel, A. and Boujelbene, Y., 2019, October. A Systematic Literature
Review of Studies on Road Congestion Modelling. In\,International
Workshop on Distributed Computing for Emerging Smart
Networks\,(pp.~23-36). Springer, Cham. Fridstrøm, L., The Case for
Marginal Cost Road Pricing in Norway.

Meloche, J.P., 2019.\,Towards a New Era in Road Pricing? Lessons from
the Experience of First Movers\,(No.~2019s-35). CIRANO.

\hypertarget{rppf}{%
\section{RPPF}\label{rppf}}

\end{document}